Adding selection to \stdpopsim: oh how the tables have turned

### 2024-11-25 analysis2_manuscript.tex

@@

    %sweeep power figure
    \begin{figure}
        \centering
        \includegraphics[width=0.8 \textwidth]{figures/sweeps/chr1_power.pdf}
        \caption{
        Power to detect selective sweeps at 100 locations along human chromosome 1 under a three population out-of-Africa model \citep{gutenkunst2009inferring}  
        with and without purifying selection acting on exons under the Gamma-distributed DFE described above. 
        The HapMap II genetic map \citep{international2007second} was used in each simulation. 
        Single beneficial mutations were introduced at each location with a selection coefficient of $s = 0.03$,
        and only sampled if they reached a terminal frequency of 0.95 or greater. 
        Three methods for detecting sweeps were used: 1) \sweepfinder \citep{degiorgio2016sweepfinder2} (top row), 
        2) \diploshic \citep{kern2018diplos} (middle row), and 3) an empirical cutoff of $\pi$ to find regions of reduced diversity (bottom row).
        True positive rate is shown for these methods for samples from the CEU and YRI samples (left and right respectively). 
        Under each method we show as a heat map exon density along the chromosome, along with the local recombination rate in cM/Mb.
        Power is shown as the proportion of replicates in which a sweep was detected at each location. 
        Each panel shows the results of simulations with purifying selection acting on exons (red; labelled BGS)
        and without purifying selection acting on exons (blue; labelled Neutral).
        }
        \label{fig:chr1_power}
    \end{figure}

@@

    \begin{figure}
        \centering
        \includegraphics[width=0.8 \textwidth]{figures/sweeps/relationship_power_cM.pdf}
        \caption{
        Power to detect selective sweeps at 100 locations along human chromosome 1 under a three population out-of-Africa model \citep{gutenkunst2009inferring}  
        with and without purifying selection as a function of local recombination rate.
        Simulations are as described in Figure \ref{fig:chr1_power}.
        Each panel shows the results of simulations with purifying selection acting on exons (red; labelled BGS)
        and without purifying selection acting on exons (blue; labelled Neutral).
        True positive rate is shown for these methods for samples from the CEU and YRI samples (left and right respectively).
        Points represent the power at each location and trend lines along with 95\% confidence intervals are shown fit to those points.
        }
        \label{fig:power-recomb}
    \end{figure}

>>>>

    % DRS: This figure could really use some Python API and comand line examples like in Figs 1B,C
    % form the original stdpopsim paper
    \begin{wrapfigure}[37]{l}{0.4\textwidth}
        \vspace{-0.0cm}
        \includegraphics[width=\linewidth]{figures/schematics/catalog.pdf}
        \caption{\label{fig:schematic}
        A schematic of the \stdpopsim catalog and the different components that
        can be used in simulations. The user specifies a species, a portion of
        the genome to simulate, and optionally a genetic map, a model of
        demography, and a model of selection that itself is composed of a
        distribution of fitness effects (DFE) and a set of functional
        annotations.}
    \end{wrapfigure}
    \hfill

@@

    %sweeep power figure
    \begin{figure}
        \centering
        \includegraphics[width=0.8 \textwidth]{figures/sweeps/chr1_power.pdf}
        \caption{
        Power to detect selective sweeps at 100 locations along human
        chromosome 1 under a three population out-of-Africa model
        \citep{gutenkunst2009inferring} when using null models with and without
        purifying selection acting on exons under the Gamma-distributed DFE
        described above.  The HapMap II genetic map
        \citep{international2007second} was used in each simulation.  Single
        beneficial mutations were introduced at each location with a selection
        coefficient of $s = 0.03$, and only sampled if they reached a terminal
        frequency of 0.95 or greater.  Three methods for detecting sweeps were
        used: 1) \sweepfinder \citep{degiorgio2016sweepfinder2} (top row), 2)
        \diploshic \citep{kern2018diplos} (middle row), and 3) an empirical
        cutoff of $\pi$ to find regions of reduced diversity (bottom row).
        True positive rate is shown for these methods for samples from the CEU
        and YRI samples (left and right respectively).  Under each method we
        show as a heat map exon density along the chromosome, along with the
        local recombination rate in cM/Mb.  Power is shown as the proportion of
        replicates in which a sweep was detected at each location.  To define
        thresholds for calling a sweep, two different null models were used: a
        neutral model (blue lines), and a model with purifying selection acting
        on exons (red lines).
        }
        \label{fig:chr1_power}
    \end{figure}

@@

    \begin{figure}
        \centering
        \includegraphics[width=0.8 \textwidth]{figures/sweeps/relationship_power_cM.pdf}
        \caption{
        Power to detect selective sweeps at 100 locations along human
        chromosome 1 under a three population out-of-Africa model
        \citep{gutenkunst2009inferring}  when using null models with and
        without purifying selection as a function of local recombination rate.
        Simulations are as described in Figure \ref{fig:chr1_power}.  True
        positive rate is shown for these methods for samples from the CEU and
        YRI samples (left and right respectively).  To define thresholds for
        calling a sweep, two different null models were used: a neutral model
        (blue lines), and a model with purifying selection acting on exons (red
        lines).  Points represent the power at each location and trend lines
        along with 95\% confidence intervals are shown fit to those points.
        }
        \label{fig:power-recomb}
    \end{figure}
